Results

### 2019-05-02 analysis/survey/preregistration.Rmd
Added details to pre-registration

3. What is the optimal mix of attributes?

@@

TODO: Add citation here maybe, or clarify the language so it's accurate

1,000 respondents constitutes a sufficient size for model estimation. A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data. We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.

@@

TODO: Explain conjoint design

@@

TODO: Explain randomization

@@

TODO: Explain statistical model

TODO: Make sure all this mathy stuff is right

TODO: Maybe specify priors?

Bayesian hierarchical multinomial logit

@@

where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.

@@

TODO: What criteria do we use?

Possibilities:

- Market simulation based on the β - determines the optimal policies
- Or look at the posteriors of the βs
- β importance - we find most important attribute + most important levels inside

>>>>

3. What is the optimal mix of attribute levels?

@@

A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data. We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample, and we had sufficient budget to acquire up to 1,000 respondents.

@@

We use a fractional factorial design. Since no single respondent can possibly see all possible combinations of the attribute levels, we create a number of different versions of the experimental design. We utilize a hierarchical Bayesian model in part to allow for information sharing across like respondents when estimating individual-level preferences for the attribute levels.

@@

Every respondent will be randomly assigned a version of the fractional factorial experimental design.

@@

We will use a hierarchical Bayesian multinomial logit model with conjugate or otherwise typical priors. The individual-level model is the multinomial logit and the upper-level model of heterogeneity is multivariate normal,

@@

where $y$ = which alternative the respondent chooses to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates, $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.

@@

TODO: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity.

We will examine the aggregate marginal posterior distributions of the attribute levels and utilize 95% credible intervals to establish "significance." Effects are "significant" if the 95% credible intervals don't include 0. Similarly, marginal posterior distributions are "significantly" different if the 95% credible intervals don't overlap.

We will examine the marginal posterior distributions of the following models:

- Organizational and structural attribute levels with an intercept-only distribution of heterogeneity
- Organizational and structural attribute levels with competing sets of covariates in the distribution of heterogeneity

Finally, we will employ the posterior distribution of model parameters to conduct counterfactual analyses via a market simulator to determine optimal policies.
